Future Virtual Particle Method for Pedestrian Navigation

### 2014-12-04 doc/informe/paper.tex
actualizo .tex
agrego explicaciones faltantes al paper.

%% LyX 2.1.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,headheight=1in,headsep=1in}
\usepackage{float}
\usepackage{amsmath}
\usepackage{graphicx}

@@

@@

\title{A Pedestrian Simulation}

\title{Future Virtual Particle Force Model}

@@

{[}Helbing 1995, 2000{]} presents a Model in which each pedestrian
feels a ``desire force'' towards his objective and a ``repulsion
force'' towards other pedestrians. On a lower level, a collission
force is present.

Collision force (Granular):

@@

\protect\caption{Fuerza de contact granular}

@@

Social Force:
\[
F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
\]

Desire Force:

Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated

@@

In each iteration, the FVP from pedestrian $i$ feels a force generated
by the other pedestrians and FVPs. First of all, we filter de pedestrians
$j$ who are not in the range of sight of pedestrian $i$ as follows:

\[
k=i+\begin{pmatrix}0 & -1\\
1 & 0
\end{pmatrix}\overrightarrow{ii'}
\]
The following must be valid:

\[
(k_{x}-i_{x})*(j_{y}-i_{y})-(k_{y}-i_{y})*(j_{x}-i_{x})>0
\]

Once filtered, the force is calculated for every other FVP. The repulsion
force between i' and j' is defined as follows:

\[
F_{ext}(i)=\sum_{j}F_{i',j'}=\sum_{j}\alpha e^{-dist(i',j')/\beta}
\]

where $\alpha$ and $\beta$ are predefined constants. Afterwards,
we calculate the repulsion force between i' and j using the same formula
but different $\alpha$ and $\beta$. Afterwards, we calculate the
force between pedestrian i and his FVP i', this is a force that pushes
i' to be in its desired relative distance from the pedestrian. This
force is represented with a spring of length ``reaction distance''
and constant $K$. When we sum all these, we get the final $F_{ext}$.

Fig 2: FVP force calculation.

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{Fuerzas que actúan sobre el Future $i'$}
\end{figure}

\begin{enumerate}
\item FVP position update.

@@

\end{itemize}
\begin{enumerate}
\item Pedestrian forces calculation.

@@

@@

Where $\tau=0.5$
\begin{enumerate}
\item Pedestrian position update.

\end{enumerate}
\end{enumerate}

@@

//TODO todos los demás parámetros

>>>>

%% LyX 2.1.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[latin9]{inputenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,headheight=1in,headsep=1in}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\numberwithin{equation}{section}
\numberwithin{figure}{section}

@@

\title{Future Virtual Particle Method for Pedestrian Navigation}

@@

{[}Helbing 1995, 2000{]} presents a Model in which each pedestrian
is subject to ``social forces''. This forces are a measure for the
internal motivations of the individual to perform certain actions.
In its simplest form, the Social Force Model consist on three main
terms. Each of there term represent a force that a pedestrian will
suffer in order to reach his objective.

The first term describes the acceleration that a pedestrian keeps
towards his desired velocity of motion. This term is known as the
``Desire Force'' and it's calculated as follows:

In this latest formula, $v_{di}$ represents the desire velocity for
the pedestrian $i$, $v_{i}$ is the current velocity and $e_{i}$
represents the desired direction of motion of the pedestrian $i$
and is calculated as follows:

\[
e_{i}(t)=\frac{r_{i}^{k}-r_{i}(t)}{||r_{i}^{k}-r_{i}(t)||}
\]

where $r_{\alpha}(t)$ denotes the actual position of the pedestrian
$i$ at the time $t$. The goal is represented as an area, and the
vector $e_{i}$ will be pointing towards the closest pont. Figure
$1.1$ shows en example of a pedestrian currenty moving in direction
of $v$ but correcting its trayectory towards $e$.

The second term represents the fact that a pedestrian keeps a certain
distance to other pedestrians and borders. This term is known as the
``Social Force'' and it's caluclated as follows:

\[
F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
\]

In this formula the terms $A$ and $B$ represents constants that
where determined by simulations and $\epsilon_{ij}$ represents the
distance from pedestrian $i$ towards pedestrian $j$. Figure $1.2$
shows this vector grafically.

The third terms represents the granular force. This force represents
the physical force that a pedestrians feels when in collision with
another objects (pedestrian or wall). This granular force term is
defined as follows:

@@

\protect\caption{Example of two pedestrians in collision}

@@

Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated for
each of the pedestrians on each simulation step and applyed to the
pedestrian until it reaches his goal.

@@

For each pedestrian $i$, the force that his future $i'$ will suffer
is calculated in this step. The magnitude of this force will depend
on two factors: by each of the other pedestrians and the walls that
might exists surronding $i$. The final value of the force applied
over the future $i'$ will be the addition of the latest two factors.

The fist factor is caluclated for each of the pedestrian $j$ ($j\neq i$).
First, we filter all pedestrians who are not in the range of sight
of pedestrian $i$. This condition is verified using the following
formula:

\[
\overrightarrow{ii'}\bullet\overrightarrow{ij'}<0
\]

This filter is represents the fact that a pedestrian (in most cases)
is not aware of what each of the pedestrians that are behind him are
doing. Hence, they are ignored. Once filtered, the pedestrian will
try to face towards the direction that think is best for avoiding
all the obstacles. This factor is represented using the social force
formula from Helbing's model.

\[
F_{ext}(i)=\sum_{j}F_{i',j'}+F_{i'j}=\sum_{j}(\alpha_{ff}e^{-dist(i',j')/\beta_{ff}}+\alpha_{fp}e^{-dist(i',j')/\beta_{fp}})
\]

where $\alpha_{x}$ and $\beta_{x}$ are predefined constants.

Here there are two terms in the $sum$. The first term represents
the fact that $i$ does not want to be in the same location as $j$
in the near future. Note that $j'$ represents the predicted location
of $j$ inferred by another pedestrian (in this case, $i$) and because
of this, it moves it's near future away of that predicted location.
The seocond term, represents the same fact but taking in mind the
current location of the pedestrian $j$. The same law applies to each
of the walls on the simulation, the difference is that the closest
point on the wall and and the future has to be calculated before applying
the formula. Also, the constants $\alpha_{fw}$ and $\beta_{fw}$
have different values.

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{External forces affecting future $i'$}
\end{figure}

Then, the desire force that pedestrian $i$ will aply to his future
is calculated. This force is modelled using two springs. The first
spring hast its origin attached on $i$ and its end attached on $i'$
and has a spring constant $K_{1}$. This spring will regulate the
velocity that will be calculated on a previous step at witch the pedestrian
$i$ will advance. The second spring, has its origin on $i'$ and
the end attached to the closest point on the pedestrian target area
and has a spring constant $K_{2}$. In order to avoid an oscilatory
movement (in example, with a single pedestrian), a damping $\gamma$
was added to this second spring. This spring represents how much te
pedestrian wants to reach his target. A larger spring constant will
force a more straight path, but possible with more collitions on its
way.

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-internal-forces}\protect\caption{Pedestrian internal forces}
\end{figure}

Because a pedestrian always tryes to reach his goal in in the sortest
possible path (hipotesis 1). If it has to take a big detour of his
ideal path, it will try to reduce his velocity drastically in order
to avoid making a long travel. In orer to recreate this fact, the
spring constant $K_{2}$ has to be variable and also dependant of
the deviation angle. This constant is defined as $K_{2}\alpha\frac{1}{\theta},$
whereas $\theta$is the angle between $\overrightarrow{ii'}$ and
$\overrightarrow{i-objective_{i}}$. The constant in this relation
is $\delta$.

After this, the final $F_{i'}$ is computed by adding all the terms.
$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$

\item FVP position update.

@@

\end{itemize}
\item Pedestrian forces calculation.

@@

Where $\tau=0.5$

\item Pedestrian position update.

@@

@@

//TODO todos los demas parametros
